%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% KEYWORDS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{longtable}[c]{|c|c|p{9.5cm}|}
\caption{Table of keywords}\\
\hline
    Lexem & Token & Description \\
\hline
\endfirsthead
\hline
    Lexem & Token & Description \\
\hline
\endhead % Encabezado para las páginas siguientes
\hline \multicolumn{3}{r}{{Continues in the next page}} \\ \hline
\endfoot % Pie de página para las páginas siguientes
\hline
\endlastfoot % Pie de página para la última página
\hline

\hline
    START & Keyword & Defines the start of the code. \\
    END & Keyword & Defines the end of the code. \\
    START\_OP & Keyword & Defines the start of a block of code. \\
    END\_OP & Keyword & Defines the end of a block of code. \\
    TO\_IMAGE & Keyword & Defines the location of an image. \\
    TO\_FOLDER & Keyword & Defines the location of a folder of images to be use. \\
    sepia & Keyword & Constant filter vintage. \\
    negative & Keyword & Constant filter, inverts colors. \\
    black\_white & Keyword & Constant filter, turns colors to black and white. \\
    dark & Keyword & Constant filter, lowers brightness. \\
    red & Keyword & Constant filter, turns colors into red. \\
    green & Keyword & Constant filter, turns colors into green. \\
    blue & Keyword & Constant filter, turns colors into blue. \\
    blur & Keyword & Constant filter, blurs an image. \\
    contour & Keyword & Constant filter, affect the shadows and glows. \\
    detail & Keyword & Constant filter, improves sharpness and brings out detail. \\
    edge & Keyword & Constant filter, sharpens edges of images. \\
    find\_edges & Keyword & Constant filter, shows mostly the edges of an image. \\
    smooth & Keyword & Constant filter, blends the pixels along the edge. \\
    sharpen & Keyword & Constant filter, focuses soft edges to increase clarity. \\
    grayscale & Keyword & Constant filter, turns colors into a greyscale. \\
    emboss & Keyword & Constant filter, darkens high-contrast edges. \\
    blur\_gaussian & Keyword & Special filter, applies a blur depending on a float. \\
    brightness & Keyword & Special enhance, rises brightness depending on a float. \\
    contrast & Keyword & Special enhance, rises contrast depending on a float. \\
    color\_enhance & Keyword & Special enhance, rises color saturation depending on a float. \\
    definition & Keyword & Special enhance, rises definition depending on a float. \\
    flip\_horizontally & Keyword & Constant transform, flips the image horizontally. \\
    flip\_vertically & Keyword & Constant transform, flips the image vertically. \\
    rotate & Keyword & Special transform, rotates depending on a integer angle (float). \\
\hline

\end{longtable}